---
title: "R Notebook"
output: html_notebook
---

#Importing libraries
```{r}
library(meta)
library(mada)
library(readxl)
library(readxl)

# For windows
setwd("D:/Dropbox/R_Files_4/COVID-19 and Radiology/COVID-19 and Radiology")

```

#CT_GGO
##Creation dataset
```{r}
data_CT_GGO_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_GGO.xlsx",
sheet = "proportion")
data_CT_GGO_proportion

metaprop_CT_GGO_proportion<-metaprop(event = data_CT_GGO_proportion$n, n = data_CT_GGO_proportion$total, data=data_CT_GGO_proportion, comb.random=TRUE, studlab=data_CT_GGO_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_GGO/CT_GGO_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_GGO_proportion,layout = "JAMA")
dev.off()
```


```{r}
data_CT_GGO_diagnostic <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_GGO.xlsx",
sheet = "diagnostic")
data_CT_GGO_diagnostic
data_CT_GGO_diagnostic$names<-data_CT_GGO_diagnostic$author

```

##Madad
```{r}
madaddata_CT_GGO_diagnostic<-madad(data_CT_GGO_diagnostic)
capture.output(print(madaddata_CT_GGO_diagnostic,digits = 2),print("Result of CT_GGO_diagnostic"),file = "CT_GGO/madaddataCT_GGO_diagnostic.txt")

modelfitdata_CT_GGO_diagnostic<-reitsma(data_CT_GGO_diagnostic)

capture.output(print(summary(modelfitdata_CT_GGO_diagnostic),digits = 3),file = "CT_GGO/summarymodel_CT_GGO_diagnostic.txt")

pdf(file="CT_GGO/sROC_plot_CT_GGO_diagnostic.pdf", width=12,height = 12)
oldpar <- par(pty="s") 
plot(modelfitdata_CT_GGO_diagnostic, predict=TRUE, cex=2)
points(x = 1-madaddata_CT_GGO_diagnostic$spec$spec, y = madaddata_CT_GGO_diagnostic$sens$sens, pch=16)
par(oldpar)
dev.off()

```


##random effect
```{r}
data_CT_GGO_diagnostic

data_CT_GGO_diagnostic$n1=data_CT_GGO_diagnostic$TP+data_CT_GGO_diagnostic$FN
data_CT_GGO_diagnostic$n2=data_CT_GGO_diagnostic$FP+data_CT_GGO_diagnostic$TN

metaprop_CT_GGO_diagnostic_sens=metaprop(event = TP, n = n1, data=data_CT_GGO_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_GGO_diagnostic$author,method = "Inverse")
metaprop_CT_GGO_diagnostic_spec=metaprop(event = TN, n = n2, data=data_CT_GGO_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_GGO_diagnostic$author,method = "Inverse")

metabin_CT_GGO_diagnostic_OR<-metabin(TP, n1, n2-TN,n2, data=data_CT_GGO_diagnostic, sm="OR",
        comb.random=TRUE,
         studlab=data_CT_GGO_diagnostic$author, method = "Inverse",
         allstudies=TRUE)



capture.output(paste(
  paste(print("Random effect of sensitivity for CT_GGO_diagnostic"),
  print(metaprop_CT_GGO_diagnostic_sens, digits = 2)),
  paste(print("Random effect of specificity for CT_GGO_diagnostic"),
  print(metaprop_CT_GGO_diagnostic_spec, digits = 2)),
  paste(print("Random effect of Diag OR for CT_GGO_diagnostic"),
  print(metabin_CT_GGO_diagnostic_OR, digits = 2))
  ),
  file = "CT_GGO/CT_GGO_diagnostic.sensitivity_specificity_DOR.txt"
  )



pdf(file="CT_GGO/Sensitivity_Plot_CT_GGO_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_GGO_diagnostic_sens,layout = "JAMA")
dev.off()


pdf(file="CT_GGO/Specificity_Plot_CT_GGO_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_GGO_diagnostic_spec,layout = "JAMA")
dev.off()


pdf(file="CT_GGO/Diagnostic_Odd_TB_CT_GGO_diagnostic.pdf", width=12,height = 12) 
forest.meta(metabin_CT_GGO_diagnostic_OR,layout = "JAMA")
dev.off()

```

#CT_GGO_Consolidation
##Creation dataset
```{r}
data_CT_GGO_Consolidation_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_GGO_Consolidation.xlsx",
sheet = "proportion")
data_CT_GGO_Consolidation_proportion

metaprop_CT_GGO_Consolidation_proportion<-metaprop(event = data_CT_GGO_Consolidation_proportion$n, n = data_CT_GGO_Consolidation_proportion$total, data=data_CT_GGO_Consolidation_proportion, comb.random=TRUE, studlab=data_CT_GGO_Consolidation_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_GGO_Consolidation/CT_GGO_Consolidation_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_GGO_Consolidation_proportion,layout = "JAMA")
dev.off()
```


```{r}
data_CT_GGO_Consolidation_diagnostic <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_GGO_Consolidation.xlsx",
sheet = "diagnostic")
data_CT_GGO_Consolidation_diagnostic
data_CT_GGO_Consolidation_diagnostic$names<-data_CT_GGO_Consolidation_diagnostic$author

```

##Madad
```{r}
madaddata_CT_GGO_Consolidation_diagnostic<-madad(data_CT_GGO_Consolidation_diagnostic)
capture.output(print(madaddata_CT_GGO_Consolidation_diagnostic,digits = 2),print("Result of CT_GGO_Consolidation_diagnostic"),file = "CT_GGO_Consolidation/madaddataCT_GGO_Consolidation_diagnostic.txt")

modelfitdata_CT_GGO_Consolidation_diagnostic<-reitsma(data_CT_GGO_Consolidation_diagnostic)

capture.output(print(summary(modelfitdata_CT_GGO_Consolidation_diagnostic),digits = 3),file = "CT_GGO_Consolidation/summarymodel_CT_GGO_Consolidation_diagnostic.txt")

pdf(file="CT_GGO_Consolidation/sROC_plot_CT_GGO_Consolidation_diagnostic.pdf", width=12,height = 12)
oldpar <- par(pty="s") 
plot(modelfitdata_CT_GGO_Consolidation_diagnostic, predict=TRUE, cex=2)
points(x = 1-madaddata_CT_GGO_Consolidation_diagnostic$spec$spec, y = madaddata_CT_GGO_Consolidation_diagnostic$sens$sens, pch=16)
par(oldpar)
dev.off()

```


##random effect
```{r}
data_CT_GGO_Consolidation_diagnostic

data_CT_GGO_Consolidation_diagnostic$n1=data_CT_GGO_Consolidation_diagnostic$TP+data_CT_GGO_Consolidation_diagnostic$FN
data_CT_GGO_Consolidation_diagnostic$n2=data_CT_GGO_Consolidation_diagnostic$FP+data_CT_GGO_Consolidation_diagnostic$TN

metaprop_CT_GGO_Consolidation_diagnostic_sens=metaprop(event = TP, n = n1, data=data_CT_GGO_Consolidation_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_GGO_Consolidation_diagnostic$author,method = "Inverse")
metaprop_CT_GGO_Consolidation_diagnostic_spec=metaprop(event = TN, n = n2, data=data_CT_GGO_Consolidation_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_GGO_Consolidation_diagnostic$author,method = "Inverse")

metabin_CT_GGO_Consolidation_diagnostic_OR<-metabin(TP, n1, n2-TN,n2, data=data_CT_GGO_Consolidation_diagnostic, sm="OR",
        comb.random=TRUE,
         studlab=data_CT_GGO_Consolidation_diagnostic$author, method = "Inverse",
         allstudies=TRUE)



capture.output(paste(
  paste(print("Random effect of sensitivity for CT_GGO_Consolidation_diagnostic"),
  print(metaprop_CT_GGO_Consolidation_diagnostic_sens, digits = 2)),
  paste(print("Random effect of specificity for CT_GGO_Consolidation_diagnostic"),
  print(metaprop_CT_GGO_Consolidation_diagnostic_spec, digits = 2)),
  paste(print("Random effect of Diag OR for CT_GGO_Consolidation_diagnostic"),
  print(metabin_CT_GGO_Consolidation_diagnostic_OR, digits = 2))
  ),
  file = "CT_GGO_Consolidation/CT_GGO_Consolidation_diagnostic.sensitivity_specificity_DOR.txt"
  )



pdf(file="CT_GGO_Consolidation/Sensitivity_Plot_CT_GGO_Consolidation_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_GGO_Consolidation_diagnostic_sens,layout = "JAMA")
dev.off()


pdf(file="CT_GGO_Consolidation/Specificity_Plot_CT_GGO_Consolidation_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_GGO_Consolidation_diagnostic_spec,layout = "JAMA")
dev.off()


pdf(file="CT_GGO_Consolidation/Diagnostic_Odd_TB_CT_GGO_Consolidation_diagnostic.pdf", width=12,height = 12) 
forest.meta(metabin_CT_GGO_Consolidation_diagnostic_OR,layout = "JAMA")
dev.off()

```





#CT_Consolidation
##Creation dataset
```{r}
data_CT_Consolidation_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Consolidation.xlsx",
sheet = "proportion")
data_CT_Consolidation_proportion

metaprop_CT_Consolidation_proportion<-metaprop(event = data_CT_Consolidation_proportion$n, n = data_CT_Consolidation_proportion$total, data=data_CT_Consolidation_proportion, comb.random=TRUE, studlab=data_CT_Consolidation_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_Consolidation/CT_Consolidation_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_Consolidation_proportion,layout = "JAMA")
dev.off()
```


```{r}
data_CT_Consolidation_diagnostic <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Consolidation.xlsx",
sheet = "diagnostic")
data_CT_Consolidation_diagnostic
data_CT_Consolidation_diagnostic$names<-data_CT_Consolidation_diagnostic$author

```

##Madad
```{r}
madaddata_CT_Consolidation_diagnostic<-madad(data_CT_Consolidation_diagnostic)
capture.output(print(madaddata_CT_Consolidation_diagnostic,digits = 2),print("Result of CT_Consolidation_diagnostic"),file = "CT_Consolidation/madaddataCT_Consolidation_diagnostic.txt")

modelfitdata_CT_Consolidation_diagnostic<-reitsma(data_CT_Consolidation_diagnostic)

capture.output(print(summary(modelfitdata_CT_Consolidation_diagnostic),digits = 3),file = "CT_Consolidation/summarymodel_CT_Consolidation_diagnostic.txt")

pdf(file="CT_Consolidation/sROC_plot_CT_Consolidation_diagnostic.pdf", width=12,height = 12)
oldpar <- par(pty="s") 
plot(modelfitdata_CT_Consolidation_diagnostic, predict=TRUE, cex=2)
points(x = 1-madaddata_CT_Consolidation_diagnostic$spec$spec, y = madaddata_CT_Consolidation_diagnostic$sens$sens, pch=16)
par(oldpar)
dev.off()

```


##random effect
```{r}
data_CT_Consolidation_diagnostic

data_CT_Consolidation_diagnostic$n1=data_CT_Consolidation_diagnostic$TP+data_CT_Consolidation_diagnostic$FN
data_CT_Consolidation_diagnostic$n2=data_CT_Consolidation_diagnostic$FP+data_CT_Consolidation_diagnostic$TN

metaprop_CT_Consolidation_diagnostic_sens=metaprop(event = TP, n = n1, data=data_CT_Consolidation_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Consolidation_diagnostic$author,method = "Inverse")
metaprop_CT_Consolidation_diagnostic_spec=metaprop(event = TN, n = n2, data=data_CT_Consolidation_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Consolidation_diagnostic$author,method = "Inverse")

metabin_CT_Consolidation_diagnostic_OR<-metabin(TP, n1, n2-TN,n2, data=data_CT_Consolidation_diagnostic, sm="OR",
        comb.random=TRUE,
         studlab=data_CT_Consolidation_diagnostic$author, method = "Inverse",
         allstudies=TRUE)



capture.output(paste(
  paste(print("Random effect of sensitivity for CT_Consolidation_diagnostic"),
  print(metaprop_CT_Consolidation_diagnostic_sens, digits = 2)),
  paste(print("Random effect of specificity for CT_Consolidation_diagnostic"),
  print(metaprop_CT_Consolidation_diagnostic_spec, digits = 2)),
  paste(print("Random effect of Diag OR for CT_Consolidation_diagnostic"),
  print(metabin_CT_Consolidation_diagnostic_OR, digits = 2))
  ),
  file = "CT_Consolidation/CT_Consolidation_diagnostic.sensitivity_specificity_DOR.txt"
  )



pdf(file="CT_Consolidation/Sensitivity_Plot_CT_Consolidation_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Consolidation_diagnostic_sens,layout = "JAMA")
dev.off()


pdf(file="CT_Consolidation/Specificity_Plot_CT_Consolidation_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Consolidation_diagnostic_spec,layout = "JAMA")
dev.off()


pdf(file="CT_Consolidation/Diagnostic_Odd_TB_CT_Consolidation_diagnostic.pdf", width=12,height = 12) 
forest.meta(metabin_CT_Consolidation_diagnostic_OR,layout = "JAMA")
dev.off()

```


#CT_Crazy_Paving
##Creation dataset
```{r}
data_CT_Crazy_Paving_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Crazy_Paving.xlsx",
sheet = "proportion")
data_CT_Crazy_Paving_proportion

metaprop_CT_Crazy_Paving_proportion<-metaprop(event = data_CT_Crazy_Paving_proportion$n, n = data_CT_Crazy_Paving_proportion$total, data=data_CT_Crazy_Paving_proportion, comb.random=TRUE, studlab=data_CT_Crazy_Paving_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_Crazy_Paving/CT_Crazy_Paving_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_Crazy_Paving_proportion,layout = "JAMA")
dev.off()
```


#CT_Halo_Sign
##Creation dataset
```{r}
data_CT_Halo_Sign_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Halo_Sign.xlsx",
sheet = "proportion")
data_CT_Halo_Sign_proportion

metaprop_CT_Halo_Sign_proportion<-metaprop(event = data_CT_Halo_Sign_proportion$n, n = data_CT_Halo_Sign_proportion$total, data=data_CT_Halo_Sign_proportion, comb.random=TRUE, studlab=data_CT_Halo_Sign_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_Halo_Sign/CT_Halo_Sign_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_Halo_Sign_proportion,layout = "JAMA")
dev.off()
```

#CT_Lymphadenopathy
##Creation dataset
```{r}
data_CT_Lymphadenopathy_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Lymphadenopathy.xlsx",
sheet = "proportion")
data_CT_Lymphadenopathy_proportion

metaprop_CT_Lymphadenopathy_proportion<-metaprop(event = data_CT_Lymphadenopathy_proportion$n, n = data_CT_Lymphadenopathy_proportion$total, data=data_CT_Lymphadenopathy_proportion, comb.random=TRUE, studlab=data_CT_Lymphadenopathy_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_Lymphadenopathy/CT_Lymphadenopathy_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_Lymphadenopathy_proportion,layout = "JAMA")
dev.off()
```


```{r}
data_CT_Lymphadenopathy_diagnostic <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Lymphadenopathy.xlsx",
sheet = "diagnostic")
data_CT_Lymphadenopathy_diagnostic
data_CT_Lymphadenopathy_diagnostic$names<-data_CT_Lymphadenopathy_diagnostic$author

```

##Madad
```{r}
madaddata_CT_Lymphadenopathy_diagnostic<-madad(data_CT_Lymphadenopathy_diagnostic)
capture.output(print(madaddata_CT_Lymphadenopathy_diagnostic,digits = 2),print("Result of CT_Lymphadenopathy_diagnostic"),file = "CT_Lymphadenopathy/madaddataCT_Lymphadenopathy_diagnostic.txt")

modelfitdata_CT_Lymphadenopathy_diagnostic<-reitsma(data_CT_Lymphadenopathy_diagnostic)

capture.output(print(summary(modelfitdata_CT_Lymphadenopathy_diagnostic),digits = 3),file = "CT_Lymphadenopathy/summarymodel_CT_Lymphadenopathy_diagnostic.txt")

pdf(file="CT_Lymphadenopathy/sROC_plot_CT_Lymphadenopathy_diagnostic.pdf", width=12,height = 12)
oldpar <- par(pty="s") 
plot(modelfitdata_CT_Lymphadenopathy_diagnostic, predict=TRUE, cex=2)
points(x = 1-madaddata_CT_Lymphadenopathy_diagnostic$spec$spec, y = madaddata_CT_Lymphadenopathy_diagnostic$sens$sens, pch=16)
par(oldpar)
dev.off()

```


##random effect
```{r}
data_CT_Lymphadenopathy_diagnostic

data_CT_Lymphadenopathy_diagnostic$n1=data_CT_Lymphadenopathy_diagnostic$TP+data_CT_Lymphadenopathy_diagnostic$FN
data_CT_Lymphadenopathy_diagnostic$n2=data_CT_Lymphadenopathy_diagnostic$FP+data_CT_Lymphadenopathy_diagnostic$TN

metaprop_CT_Lymphadenopathy_diagnostic_sens=metaprop(event = TP, n = n1, data=data_CT_Lymphadenopathy_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Lymphadenopathy_diagnostic$author,method = "Inverse")
metaprop_CT_Lymphadenopathy_diagnostic_spec=metaprop(event = TN, n = n2, data=data_CT_Lymphadenopathy_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Lymphadenopathy_diagnostic$author,method = "Inverse")

metabin_CT_Lymphadenopathy_diagnostic_OR<-metabin(TP, n1, n2-TN,n2, data=data_CT_Lymphadenopathy_diagnostic, sm="OR",
        comb.random=TRUE,
         studlab=data_CT_Lymphadenopathy_diagnostic$author, method = "Inverse",
         allstudies=TRUE)



capture.output(paste(
  paste(print("Random effect of sensitivity for CT_Lymphadenopathy_diagnostic"),
  print(metaprop_CT_Lymphadenopathy_diagnostic_sens, digits = 2)),
  paste(print("Random effect of specificity for CT_Lymphadenopathy_diagnostic"),
  print(metaprop_CT_Lymphadenopathy_diagnostic_spec, digits = 2)),
  paste(print("Random effect of Diag OR for CT_Lymphadenopathy_diagnostic"),
  print(metabin_CT_Lymphadenopathy_diagnostic_OR, digits = 2))
  ),
  file = "CT_Lymphadenopathy/CT_Lymphadenopathy_diagnostic.sensitivity_specificity_DOR.txt"
  )



pdf(file="CT_Lymphadenopathy/Sensitivity_Plot_CT_Lymphadenopathy_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Lymphadenopathy_diagnostic_sens,layout = "JAMA")
dev.off()


pdf(file="CT_Lymphadenopathy/Specificity_Plot_CT_Lymphadenopathy_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Lymphadenopathy_diagnostic_spec,layout = "JAMA")
dev.off()


pdf(file="CT_Lymphadenopathy/Diagnostic_Odd_TB_CT_Lymphadenopathy_diagnostic.pdf", width=12,height = 12) 
forest.meta(metabin_CT_Lymphadenopathy_diagnostic_OR,layout = "JAMA")
dev.off()

```

#CT_Nodule
##Creation dataset
```{r}
data_CT_Nodule_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Nodule.xlsx",
sheet = "proportion")
data_CT_Nodule_proportion

metaprop_CT_Nodule_proportion<-metaprop(event = data_CT_Nodule_proportion$n, n = data_CT_Nodule_proportion$total, data=data_CT_Nodule_proportion, comb.random=TRUE, studlab=data_CT_Nodule_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_Nodule/CT_Nodule_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_Nodule_proportion,layout = "JAMA")
dev.off()
```


```{r}
data_CT_Nodule_diagnostic <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Nodule.xlsx",
sheet = "diagnostic")
data_CT_Nodule_diagnostic
data_CT_Nodule_diagnostic$names<-data_CT_Nodule_diagnostic$author

```

##Madad
```{r}
madaddata_CT_Nodule_diagnostic<-madad(data_CT_Nodule_diagnostic)
capture.output(print(madaddata_CT_Nodule_diagnostic,digits = 2),print("Result of CT_Nodule_diagnostic"),file = "CT_Nodule/madaddataCT_Nodule_diagnostic.txt")

modelfitdata_CT_Nodule_diagnostic<-reitsma(data_CT_Nodule_diagnostic)

capture.output(print(summary(modelfitdata_CT_Nodule_diagnostic),digits = 3),file = "CT_Nodule/summarymodel_CT_Nodule_diagnostic.txt")

pdf(file="CT_Nodule/sROC_plot_CT_Nodule_diagnostic.pdf", width=12,height = 12)
oldpar <- par(pty="s") 
plot(modelfitdata_CT_Nodule_diagnostic, predict=TRUE, cex=2)
points(x = 1-madaddata_CT_Nodule_diagnostic$spec$spec, y = madaddata_CT_Nodule_diagnostic$sens$sens, pch=16)
par(oldpar)
dev.off()

```


##random effect
```{r}
data_CT_Nodule_diagnostic

data_CT_Nodule_diagnostic$n1=data_CT_Nodule_diagnostic$TP+data_CT_Nodule_diagnostic$FN
data_CT_Nodule_diagnostic$n2=data_CT_Nodule_diagnostic$FP+data_CT_Nodule_diagnostic$TN

metaprop_CT_Nodule_diagnostic_sens=metaprop(event = TP, n = n1, data=data_CT_Nodule_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Nodule_diagnostic$author,method = "Inverse")
metaprop_CT_Nodule_diagnostic_spec=metaprop(event = TN, n = n2, data=data_CT_Nodule_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Nodule_diagnostic$author,method = "Inverse")

metabin_CT_Nodule_diagnostic_OR<-metabin(TP, n1, n2-TN,n2, data=data_CT_Nodule_diagnostic, sm="OR",
        comb.random=TRUE,
         studlab=data_CT_Nodule_diagnostic$author, method = "Inverse",
         allstudies=TRUE)



capture.output(paste(
  paste(print("Random effect of sensitivity for CT_Nodule_diagnostic"),
  print(metaprop_CT_Nodule_diagnostic_sens, digits = 2)),
  paste(print("Random effect of specificity for CT_Nodule_diagnostic"),
  print(metaprop_CT_Nodule_diagnostic_spec, digits = 2)),
  paste(print("Random effect of Diag OR for CT_Nodule_diagnostic"),
  print(metabin_CT_Nodule_diagnostic_OR, digits = 2))
  ),
  file = "CT_Nodule/CT_Nodule_diagnostic.sensitivity_specificity_DOR.txt"
  )



pdf(file="CT_Nodule/Sensitivity_Plot_CT_Nodule_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Nodule_diagnostic_sens,layout = "JAMA")
dev.off()


pdf(file="CT_Nodule/Specificity_Plot_CT_Nodule_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Nodule_diagnostic_spec,layout = "JAMA")
dev.off()


pdf(file="CT_Nodule/Diagnostic_Odd_TB_CT_Nodule_diagnostic.pdf", width=12,height = 12) 
forest.meta(metabin_CT_Nodule_diagnostic_OR,layout = "JAMA")
dev.off()

```


#CT_Pleural_Effusion
##Creation dataset
```{r}
data_CT_Pleural_Effusion_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Pleural_Effusion.xlsx",
sheet = "proportion")
data_CT_Pleural_Effusion_proportion

metaprop_CT_Pleural_Effusion_proportion<-metaprop(event = data_CT_Pleural_Effusion_proportion$n, n = data_CT_Pleural_Effusion_proportion$total, data=data_CT_Pleural_Effusion_proportion, comb.random=TRUE, studlab=data_CT_Pleural_Effusion_proportion$author,pscale = 100,method = "Inverse")

pdf(file="CT_Pleural_Effusion/CT_Pleural_Effusion_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_CT_Pleural_Effusion_proportion,layout = "JAMA")
dev.off()
```


```{r}
data_CT_Pleural_Effusion_diagnostic <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_CT_Pleural_Effusion.xlsx",
sheet = "diagnostic")
data_CT_Pleural_Effusion_diagnostic
data_CT_Pleural_Effusion_diagnostic$names<-data_CT_Pleural_Effusion_diagnostic$author

```

##Madad
```{r}
madaddata_CT_Pleural_Effusion_diagnostic<-madad(data_CT_Pleural_Effusion_diagnostic)
capture.output(print(madaddata_CT_Pleural_Effusion_diagnostic,digits = 2),print("Result of CT_Pleural_Effusion_diagnostic"),file = "CT_Pleural_Effusion/madaddataCT_Pleural_Effusion_diagnostic.txt")

modelfitdata_CT_Pleural_Effusion_diagnostic<-reitsma(data_CT_Pleural_Effusion_diagnostic)

capture.output(print(summary(modelfitdata_CT_Pleural_Effusion_diagnostic),digits = 3),file = "CT_Pleural_Effusion/summarymodel_CT_Pleural_Effusion_diagnostic.txt")

pdf(file="CT_Pleural_Effusion/sROC_plot_CT_Pleural_Effusion_diagnostic.pdf", width=12,height = 12)
oldpar <- par(pty="s") 
plot(modelfitdata_CT_Pleural_Effusion_diagnostic, predict=TRUE, cex=2)
points(x = 1-madaddata_CT_Pleural_Effusion_diagnostic$spec$spec, y = madaddata_CT_Pleural_Effusion_diagnostic$sens$sens, pch=16)
par(oldpar)
dev.off()

```


##random effect
```{r}
data_CT_Pleural_Effusion_diagnostic

data_CT_Pleural_Effusion_diagnostic$n1=data_CT_Pleural_Effusion_diagnostic$TP+data_CT_Pleural_Effusion_diagnostic$FN
data_CT_Pleural_Effusion_diagnostic$n2=data_CT_Pleural_Effusion_diagnostic$FP+data_CT_Pleural_Effusion_diagnostic$TN

metaprop_CT_Pleural_Effusion_diagnostic_sens=metaprop(event = TP, n = n1, data=data_CT_Pleural_Effusion_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Pleural_Effusion_diagnostic$author,method = "Inverse")
metaprop_CT_Pleural_Effusion_diagnostic_spec=metaprop(event = TN, n = n2, data=data_CT_Pleural_Effusion_diagnostic,
        comb.random=TRUE,
         studlab=data_CT_Pleural_Effusion_diagnostic$author,method = "Inverse")

metabin_CT_Pleural_Effusion_diagnostic_OR<-metabin(TP, n1, n2-TN,n2, data=data_CT_Pleural_Effusion_diagnostic, sm="OR",
        comb.random=TRUE,
         studlab=data_CT_Pleural_Effusion_diagnostic$author, method = "Inverse",
         allstudies=TRUE)



capture.output(paste(
  paste(print("Random effect of sensitivity for CT_Pleural_Effusion_diagnostic"),
  print(metaprop_CT_Pleural_Effusion_diagnostic_sens, digits = 2)),
  paste(print("Random effect of specificity for CT_Pleural_Effusion_diagnostic"),
  print(metaprop_CT_Pleural_Effusion_diagnostic_spec, digits = 2)),
  paste(print("Random effect of Diag OR for CT_Pleural_Effusion_diagnostic"),
  print(metabin_CT_Pleural_Effusion_diagnostic_OR, digits = 2))
  ),
  file = "CT_Pleural_Effusion/CT_Pleural_Effusion_diagnostic.sensitivity_specificity_DOR.txt"
  )



pdf(file="CT_Pleural_Effusion/Sensitivity_Plot_CT_Pleural_Effusion_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Pleural_Effusion_diagnostic_sens,layout = "JAMA")
dev.off()


pdf(file="CT_Pleural_Effusion/Specificity_Plot_CT_Pleural_Effusion_diagnostic.pdf", width=12,height = 12) 
forest.meta(metaprop_CT_Pleural_Effusion_diagnostic_spec,layout = "JAMA")
dev.off()


pdf(file="CT_Pleural_Effusion/Diagnostic_Odd_TB_CT_Pleural_Effusion_diagnostic.pdf", width=12,height = 12) 
forest.meta(metabin_CT_Pleural_Effusion_diagnostic_OR,layout = "JAMA")
dev.off()

```

#Xray_Consolidation
##Creation dataset
```{r}
data_Xray_Consolidation_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_Xray_Consolidation.xlsx",
sheet = "proportion")
data_Xray_Consolidation_proportion

metaprop_Xray_Consolidation_proportion<-metaprop(event = data_Xray_Consolidation_proportion$n, n = data_Xray_Consolidation_proportion$total, data=data_Xray_Consolidation_proportion, comb.random=TRUE, studlab=data_Xray_Consolidation_proportion$author,pscale = 100,method = "Inverse")

pdf(file="Xray_Consolidation/Xray_Consolidation_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_Xray_Consolidation_proportion,layout = "JAMA")
dev.off()
```


#Xray_GGO
##Creation dataset
```{r}
data_Xray_GGO_proportion <- read_excel("D:/Dropbox/R_Files_4/COVID-19 and Radiology/Consensus_Xray_GGO.xlsx",
sheet = "proportion")
data_Xray_GGO_proportion

metaprop_Xray_GGO_proportion<-metaprop(event = data_Xray_GGO_proportion$n, n = data_Xray_GGO_proportion$total, data=data_Xray_GGO_proportion, comb.random=TRUE, studlab=data_Xray_GGO_proportion$author,pscale = 100,method = "Inverse")

pdf(file="Xray_GGO/Xray_GGO_proportion.pdf", width=8,height = 12) 
forest.meta(metaprop_Xray_GGO_proportion,layout = "JAMA")
dev.off()
```

